---
title: "p8105_hw5_yw3995"
author: "Yuxuan Wang"
date: "2023-11-11"
output: github_document
---

```{r, message = FALSE}
library(readr)
library(tidyverse)
library(rvest)
library(ggplot2)
```

# Problem 1

```{r, message = FALSE}
raw_data = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

raw_data = read.csv(raw_data)
```

* Raw data describe the homicides in 50 large U.S. cities, which contains **`r ncol(raw_data)`** variables and **`r nrow(raw_data)`** observations.
* Raw data has lots of variables, such as: `r names(raw_data)`, and the key variables are **city, state, disposition**.

```{r, message = FALSE}
tidy_data =
  raw_data |> 
  mutate(city_state = paste(city, state, sep = ", ")) |> 
  group_by(city_state) |> 
  summarise(
    total_homicides = n(), 
    unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))  
  )

tidy_data = tidy_data[tidy_data$city_state != "Tulsa, AL", ] 

tidy_data
```

```{r, message = FALSE}
baltimore_df = raw_data |> 
  mutate(city_state = paste(city, state, sep = ", ")) |> 
  mutate(disposition = ifelse(disposition == "Closed by arrest", "homicides", "unsolved_homicides")) |> 
  filter(city_state == "Baltimore, MD")

baltimore_result = prop.test(x = sum(baltimore_df$disposition %in% c("unsolved_homicides")), n = nrow(baltimore_df), correct = FALSE)

baltimore_result_tidy = broom::tidy(baltimore_result) |> 
  mutate(confidence_intervals = paste(conf.low, conf.high, sep = ", ")) |> 
  rename(estimated_proportion = estimate) |> 
  select(estimated_proportion, confidence_intervals) 

baltimore_result_tidy
```

```{r, message = FALSE}
city_df = tidy_data |> 
  mutate(
    city_test_result = map2(unsolved_homicides, total_homicides, ~prop.test(x = .x, n = .y)),
    city_tidy_result = map(city_test_result, broom::tidy)
  ) |> 
  select(city_state, city_tidy_result) |> 
  unnest(city_tidy_result) |> 
  select(city_state, estimate, conf.low, conf.high) 


city_tidy_df = city_df |> 
  mutate(confidence_intervals = paste(conf.low, conf.high, sep = ", ")) |> 
  rename(estimated_proportion = estimate) |> 
  select(city_state, estimated_proportion, confidence_intervals)

city_tidy_df
```

```{r, message = FALSE}
ggplot(city_df, aes(x = reorder(city_state, estimate), y = estimate)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, color = "red") +
  coord_flip() +  
  labs(x = "City",
       y = "Estimated Proportion of Unsolved Homicides",
       title = "Estimates and Confidence Intervals by City") +
  theme_minimal()
```

# Problem 2

```{r, message = FALSE}
file_names = list.files(path = "./data/", full.names = TRUE)

files_df = data.frame(file_path = file_names) |>
  mutate(file_name = basename(file_path),
         arm = sub("_.*", "", file_name), 
         subject_id = sub(".*_", "", sub("\\..*", "", file_name))) 

read_data = function(file_path) {
  read_csv(file_path) |>
    gather(key = "week", value = "observation") 
}

tidy_data_q2 = files_df |>
  mutate(data = map(file_path, read_data)) |> 
  unnest(data) |> 
  mutate(week = as.numeric(gsub("week_", "", week))) |> 
  select(arm, subject_id, week, observation) |> 
  select(subject_id, everything())

tidy_data_q2
```

```{r, message = FALSE}
spaghetti_plot = ggplot(tidy_data_q2, aes(x = week, y = observation, color = subject_id)) +
  geom_point() +
  geom_line() +
  facet_wrap(~arm) +
  labs(
    x = "Week",
    y = "Observation",
    title = "Spaghetti Plot of Observations on Each Subject Over Time",
    color = "subject_id"
  ) +
  theme_minimal()

spaghetti_plot
```
 
* In the `con` (control) group, we observe that weekly observations **consistent fluctuations** within the **range of -1.25 to 3.75**. However, in the `exp` (experimental) group, we can see a **weekly increase** in observations of approximately **3.125**.